### 2021-07-07 rad-icfp-2021/complexity.tex
typo

We define the nesting of array operations $\NestA$ of a term !e! of Source by induction as follows.

@@

After that, the proof is by routine induction on !e!. 
First, one computes the cost of $\directD{\rho}{\Gamma}{Y}$(!e!).
It has $N$ too many MOVES which are removed by inlining and forward substitution using the invariant that at each step, 
at most 2 !x!$_i$ in the continuation are not variables.
\end{proof}

>>>>

We define the nesting of array operations $\NestA$ of a term !e! of Source by induction on !e! as follows.

@@

After that, the proof is by routine induction on !e!. 
First, one computes the cost of $\directD{\rho}{\Gamma}{Y}$(!e!).
It has $n$ too many MOVES which are removed by inlining and forward substitution using the invariant that at each step, 
at most 2 !x!$_i$ in the continuation are not variables.
\end{proof}
